Software Ticket Quality

### 2017-10-30 proposal/mprop.tex
Add organizational impact of information quality paper

>>>>

\textbf{Organizational Impact of 
        Information Quality}\cite{gorla2010organizational}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors had two main research questions they wanted to address:
      \begin{itemize}
        \item what individual/combined influences system quality, service quality,
          information quality have on organizational impact?
        \item what effect does system quality have on information quality?
      \end{itemize}
  \item \textbf{What was the method?}
    They conducted a construct measurement for the IS quality dimensions and 
    collected data through empirical testing.
  \item \textbf{What did they learn?}
    Firstly, they learned that service quality has the greatest impact 
    of all three quality constructs. Moreover, they found out that there is a 
    linkage between system and information quality, fact that previous research
    did not reveal. Lastly, their results indicate that the above-mentioned 
    quality dimensions have a significant positive influence on organizational
    impact either directly or indirectly.
  \item \textbf{Relevance to our work}: the paper can provide us insights into
    how valuable information quality is and what an impact it can have.
\end{itemize}
